Class Notes

### 2021-07-26 latex-teaching/notes.tex
Cleaned up

@@

>>>>

\newcommand{\foo}{\color{heading}\makebox[0pt]{\textbullet}\hskip-0.5pt\vrule width 1pt\hspace{\labelsep}}

\newtcolorbox[blend into=figures]{myfigure}[2][]{
    enhanced,
    attach boxed title to top left={
        yshift=0.2mm
    },
    top=1.5em,
    colback=white,
    colframe=white,
    fonttitle=\bfseries,
    boxed title style={
        sharp corners,
        size=small,
        colback=indigo,
        colframe=indigo
    },
    borderline north={0.5mm}{0mm}{line width=3pt},
    float, title=#2, #1
}

@@

\begin{myfigure}{Duck}
    \includegraphics{example-image-duck}

    \tcblower
    \textbf{Notes:} A band limited signal cannot be time limited and a time-limited signal cannot be band limited and options.
\end{myfigure}

\begin{table}
    \renewcommand\arraystretch{2}
    \caption{Timeline}

    \begin{tabular}{@{}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash} p{10cm}@{}}
    \addlinespace[1.5ex]
    1947 & AT and T Bell Labs develop the idea of cellular phones\\
    1968 & Xerox Palo Alto Research Centre envisage the 'Dynabook\\
    1971 & Busicom 'Handy-LE' Calculator\\
    1973 & First mobile handset invented by Martin Cooper\\
    1978 & Parker Bros. Merlin Computer Toy\\
    1981 & Osborne 1 Portable Computer\\
    1982 & Grid Compass 1100 Clamshell Laptop\\
    1983 & TRS-80 Model 100 Portable PC\\
    1984 & Psion Organiser Handheld Computer\\
    1991 & Psion Series 3 Minicomputer\\
    \end{tabular}
\end{table}
